SMASH companion source code repository

### 2018-12-20 analysis/index.Rmd
wflow_publish("index.Rmd")

See [here][gtexresults] for the source repository. This is what
you will find in the repository:

```
├── analysis
├── code
├── data
├── docs
├── output
└── workflows
```

+ The **analysis** contains R Markdown source files for the workflowr
  website, including R code used in the final step of the analysis to
  generate figures and tables for the manuscript.

+ The **code** directory contains additional supporting code for the
  analyses.

+ The **data** directory contains original and processed data files
  used in the mash analysis of the GTEx data, example data sets used
  to illustrate the data processing and analysis pipelines, and
  additional data used to generate the tables and figures for the
  manuscript.

+ The **docs** directory contains webpages generated from the R
  Markdown files in the analysis directory.

+ The **output** stores outputs from data processing and analysis
  pipelines ("workflows").

+ The **workflows** directory contains source code ("SoS workflows")
  and Docker configuration files ("Dockerfiles") implementing a data
  processing pipeline for mash and an end-to-end analysis of the GTEx
  data using the multivariate statistical methods ("mash").

>>>>

See [here][smash-github] for the source repository. This is the
overall structure of the repository:

```
├── analysis
├── code
├── data
├── docs
├── dsc
├── output
└── shiny
```

+ The `analysis` directory contains R Markdown source files for the
  workflowr website, including R code implementing the SMASH demos,
  and R code to generate tables and figures for the manuscript.

+ The `code` directory contains additional supporting code for the
  demos and analyses of the results.

+ The `data` directory contains data files used in the ChIP-seq demo.

+ The `docs` directory contains webpages generated from the R
  Markdown files in the analysis directory.

+ The `dsc` directory contains R and MATLAB code used to implement the
  "Gaussian mean estimation" simulations in the manuscript.

+ The `output` directory contains results from the Gaussian and
  Poisson simulations.

+ The `shiny` directory contains code to generate the Shiny
  Web app in R.
